---
title: "Sex and gender as prognostic factors for outcomes among living kidney donors: A Systematic Review"
format:
    html:
      toc-title: Table of contents
      toc: true
      toc-depth: 5
      highlight-style: github
      toc-location: left
      page-layout: full
      embed-resources: true
      self-contained-math: true
editor: visual
date: "14 Sept 2026"
execute:
  echo: false
toc: true
toc-depth: 5
---

::: {.content-hidden when-format="html"}
## Data and package

```{r, message=FALSE, warning=FALSE, echo=TRUE, include=FALSE}
# Check libraries, install missing packages, update old packages, and load packages
libs <- c("dplyr", "tidyr", "readxl","ggplot2", "ggplotify", "meta", "metafor", "ggpubr", "writexl")

# # Install packages at once
# missing <- !libs %in% installed.packages()
# if (any(missing)) {
#   install.packages(libs[missing])
# }

lapply(libs, library, character.only = TRUE)

# Jiayue's working directory
setwd("/Users/jwan0349/Library/CloudStorage/OneDrive-TheUniversityofSydney(Staff)(2)/CKR/21-Prognosis_Meta-Analysis/Meta-Analysis-Donor-sex-as-a-prognostic-factor-for-post-donation-outcomes")

# Eswari's working directory
# setwd(C":/Users/dreswarivilayur/OneDrive/phd proposal/prognosis factor review/METANALYSIS DATA_new_latest.xlsx")

```
:::

------------------------------------------------------------------------

## Outcomes

### 1) Risk of GFR \< 60mls/min, Male vs Female

```{r}
# Read data into R
df_gfr <- read_xlsx("METANALYSIS DATA_new_latest.xlsx",
                  sheet = "gfr_data", skip = 1) %>% 
  filter(outcome == 2) %>% 
  mutate( 
    
    # Data preparation
    study_n = trimws(as.character(study_n)),
    e_men = as.numeric(e_men), 
    ne_men = as.numeric(ne_men), 
    e_women = as.numeric(e_women), 
    ne_women = as.numeric(ne_women),
    fu_time_cat = as.factor(if_else(f_up %in% c("1yr", "6m"), "1 yr", "Longer than 1 yr")),
    Era = factor(case_when(
      study_n %in% c("#7315", "#7472", "#7972") ~ "2021-2026",
      TRUE ~ "2011-2020")),
    Era = relevel(Era, ref = "2011-2020"),
    Region = factor(case_when(study_n %in% c("#3393", "#7472", "#5084") ~ "Europe and Central Asia",
                              study_n %in% c("#2347") ~ "Latin America and Carribean",
                              study_n %in% c("#879", "#5950", "#7315") ~ "East Asia and Pacific",
                              TRUE ~ "South Asia"))
  ) 
```

```{r, fig.width=8, fig.height=5}
m_gfr <- metabin(
  event.e = e_men,
  n.e = total_men,
  event.c = e_women,
  n.c = total_women,
  studlab = study_id,
  data = df_gfr,

  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_gfr)
```

#### Forest plot

```{r, fig.height=4, fig.width=12, warning=FALSE}
fp_gfr <- as.ggplot(~ forest(
  m_gfr,
  
  # Selecte columns to be presented
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  # Label the columns
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  
  # Selecte columns to be presented
  rightcols = c("effect", "ci", "w.random"),
  # Label the columns
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE, digits = 2, digits.sd = 2, digits.mean = 2, digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square = "#82abc4",
  col.diamond = "#285980",
  col.study.ci = "black",
  col.inside = "black"
))

fp_gfr

# ggsave("Plots/fp_gfr.pdf", fp_gfr, width = 12, height = 4, bg = "white")
```

##### Dataframe

```{r}
# Save the results to a dataframe to be exported later
df_fp_gfr <- m_gfr$data %>%
  mutate(
    OR = exp(m_gfr$TE),
    lower_CI = exp(m_gfr$lower),
    upper_CI = exp(m_gfr$upper),
    weight_random = weights(m_gfr)$p.random
  ) %>%
  transmute(
    Study = study_id,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
  )
```

------------------------------------------------------------------------

#### Stratify by follow-up time

```{r}
m_gfr_fu <- metabin(
  event.e = e_men,
  n.e = total_men,
  event.c = e_women,
  n.c = total_women,
  studlab = study_id,
  data = df_gfr,
  subgroup = fu_time_cat,

  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

m_gfr_fu
```

-   **Subgroup differences p value = 0.2215, indicates there is NO significant differences of sex among subgroups (follow up time within 1 year v.s. follow up time longer than 1 year).**

-   **Heterogeneity within the subgroup of FU time \> 1 yr.**: $I^2$ = 64.2%

-   **OR is significant in the subgroup of FU time \> 1 yr: 2.9263 \[1.4420, 5.9386\].**

------------------------------------------------------------------------

#### Stratify by era

```{r}
m_gfr_era <- metabin(
  event.e = e_men,
  n.e = total_men,
  event.c = e_women,
  n.c = total_women,
  studlab = study_id,
  data = df_gfr,
  subgroup = Era,

  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

m_gfr_era
```

##### Forest plot

```{r, fig.height=6, fig.width=12, warning=FALSE}
fp_gfr_era <- as.ggplot(~ forest(
  m_gfr_era,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_gfr_era

# ggsave("Plots/fp_gfr_era.pdf", fp_gfr_era, width = 12, height = 6, bg = "white")
```

##### Dataframe

```{r}
df_fp_gfr_era <- m_gfr_era$data %>%
  mutate(
    OR = exp(m_gfr$TE),
    lower_CI = exp(m_gfr$lower),
    upper_CI = exp(m_gfr$upper),
    weight_random = weights(m_gfr)$p.random
  ) %>%
  transmute(
    Study = study_id,
    Era = Era,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
  )
```

#### By region

```{r}
m_gfr_region <- metabin(
  event.e = e_men,
  n.e = total_men,
  event.c = e_women,
  n.c = total_women,
  studlab = study_id,
  data = df_gfr,
  subgroup = Region,

  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

m_gfr_region
```

##### Forest plot

```{r, fig.height=7, fig.width=12, warning=FALSE}
fp_gfr_region <- as.ggplot(~ forest(
  m_gfr_region,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE, 
  digits = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square = "#82abc4",
  col.diamond = "#285980",
  col.study.ci = "black",
  col.inside = "black"
))

fp_gfr_region

# ggsave("Plots/fp_gfr_region.pdf", fp_gfr_region, width = 12, height = 7, bg = "white")
```

#### Dataframe

```{r}
df_fp_gfr_region <- m_gfr_region$data %>%
  mutate(
    OR = exp(m_gfr$TE),
    lower_CI = exp(m_gfr$lower),
    upper_CI = exp(m_gfr$upper),
    weight_random = weights(m_gfr)$p.random
  ) %>%
  transmute(
    Study = study_id,
    Region = Region,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
  )
```

#### SA: Excluding "Patel, 2013"

```{r}
df_gfr_sa <- df_gfr %>%
  filter(study_id != "Patel, 2013")

m_gfr_sa <- metabin(
  event.e = e_men,
  n.e = total_men,
  event.c = e_women,
  n.c = total_women,
  studlab = study_id,
  data = df_gfr_sa,

  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_gfr_sa)
```

##### Forest plot

```{r, fig.height=4, fig.width=12, warning=FALSE}
fp_gfr_sa <- as.ggplot(~ forest(
  m_gfr_sa,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE, digits = 2, digits.sd = 2, digits.mean = 2, digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square = "#82abc4",
  col.diamond = "#285980",
  col.study.ci = "black",
  col.inside = "black"
))

fp_gfr_sa

# ggsave("Plots/fp_gfr_sa.pdf", fp_gfr_sa, width = 12, height = 4, bg = "white")
```

------------------------------------------------------------------------

### 2) Mortality: Male vs Female

```{r}
mor_data <- read_xlsx("METANALYSIS DATA_new_latest.xlsx", 
                 sheet = "mor_data", skip = 1) %>%
  
  # Select only valid columns
  select(c(1:19)) %>%
  filter(!is.na(study_id) & outcome == 2) %>%
  
  # Convert required columns from character to numerical
  mutate(across(c(9:10, 17:19), as.numeric)) %>%
  mutate(
    TE = log(hr_mor),
    seTE = (log(upper_CI) - log(lower_CI)) / (2 * 1.96),
    high_rob = if_else(study_n %in% c("#7054"), 1, 0)
  )
```

```{r}
m_mor_hr <- metagen(
  TE = TE,
  seTE = seTE,
  studlab = study_id,
  data = mor_data,
  sm = "HR",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_mor_hr)
```

#### Forest plot

```{r, fig.height=4, fig.width=12, warning=FALSE}
fp_death <- as.ggplot(~ forest(
  m_mor_hr,
  leftcols = c("studlab", "follow_up", "e_men", "total_men", "e_women", "total_women"),
  leftlabs = c("Study", "Follow-up\nperiod (years)", "Male\nEvents", "Male\nTotal", "Female\nEvents", "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Hazard Ratio\n(Male vs Female)", "95% CI", "Weight"),
  smlab = "Hazard Ratio\n(Male vs Female)",
  colgap = "4mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE, digits = 2, digits.sd = 2, digits.mean = 2, digits.weight = 2,
  overall.hetstat = TRUE,
  col.square = "#82abc4",
  col.diamond = "#285980",
  col.study.ci = "black",
  col.inside = "black"
))

fp_death

# ggsave("Plots/fp_death.pdf", fp_death, width = 12, height = 4, bg = "white")
```

##### Dataframe

```{r}
df_fp_mor <- m_mor_hr$data %>%
  mutate(
    HR = exp(m_mor_hr$TE),
    lower_CI = exp(m_mor_hr$lower),
    upper_CI = exp(m_mor_hr$upper),
    weight_random = weights(m_mor_hr)$p.random
  ) %>%
  transmute(
    Study = study_id,
    `Follow-up period (years)` = follow_up,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Hazard Ratio (Male vs Female)` = round(HR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
  )
```

#### SA excluding high RoB

```{r}
mor_data_sa <- mor_data %>%
  filter(high_rob == 0) # Exclude studies with high RoB

m_mor_sa <- metagen(
  TE = TE,
  seTE = seTE,
  studlab = study_id,
  data = mor_data_sa,
  sm = "HR",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_mor_sa)
```

#### Forest plot

```{r, fig.height=4, fig.width=12, warning=FALSE}
fp_death_sa <- as.ggplot(~ forest(
  m_mor_sa,
  leftcols = c("studlab", "follow_up", "e_men", "total_men", "e_women", "total_women"),
  leftlabs = c("Study", "Follow-up\nperiod (years)", "Male\nEvents", "Male\nTotal", "Female\nEvents", "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Hazard Ratio\n(Male vs Female)", "95% CI", "Weight"),
  smlab = "Hazard Ratio\n(Male vs Female)",
  colgap = "4mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE, digits = 2, digits.sd = 2, digits.mean = 2, digits.weight = 2,
  overall.hetstat = TRUE,
  col.square = "#82abc4",
  col.diamond = "#285980",
  col.study.ci = "black",
  col.inside = "black"
))

fp_death_sa

# ggsave("Plots/fp_death_sa.pdf", fp_death_sa, width = 12, height = 4, bg = "white")
```

##### Dataframe

```{r}
df_fp_mor_sa <- m_mor_sa$data %>%
  mutate(
    HR = exp(m_mor_sa$TE),
    lower_CI = exp(m_mor_sa$lower),
    upper_CI = exp(m_mor_sa$upper),
    weight_random = weights(m_mor_sa)$p.random
  ) %>%
  transmute(
    Study = study_id,
    `Follow-up period (years)` = follow_up,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Hazard Ratio (Male vs Female)` = round(HR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
  )
```

------------------------------------------------------------------------

### 3) Kidney failure

#### Primary

```{r}
kf_data <- read_xlsx("METANALYSIS DATA_new_latest.xlsx",
                 sheet = "kf_data_new", 
                 skip = 1) %>%
  filter(!is.na(study_id)) %>%
  mutate(high_rob = if_else(study_id %in% c("Gibney, 2008", "Matas, 2018", "Rizvi, 2016", "Kim, 2020"), 1, 0))
  # filter(study_id != "Matas, 2018")

m_kf <- metabin(
  event.e = e_male,
  n.e     = total_male,
  event.c = e_female,
  n.c     = total_female,
  studlab = study_id,
  data    = kf_data,

  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_kf)
```

##### Forest plot

```{r, fig.height=3, fig.width=12, warning=FALSE}
fp_kf <- as.ggplot(~ forest(
  m_kf,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_kf

# ggsave("Plots/fp_kf.pdf", fp_kf, width = 12, height = 4.5, bg = "white")
```

##### Dataframe

```{r}
df_fp_kf <- m_kf$data %>%
  mutate(
    OR = exp(m_kf$TE),
    lower_CI = exp(m_kf$lower),
    upper_CI = exp(m_kf$upper),
    weight_random = weights(m_kf)$p.random
  ) %>%
  transmute(
    Study = study_id,
    `Male Events` = e_male,
    `Male Total` = total_male,
    `Female Events` = e_female,
    `Female Total` = total_female,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
  )
```

### 4) Surgical complications

```{r}
surcom_data <- read_xlsx("METANALYSIS DATA_new_latest.xlsx",
                 sheet = "surcom_data", skip = 1) %>% 
  filter(outcome == 2) %>%
  mutate(across(c(e_men, total_men, e_women, total_women), as.numeric),
         high_rob = if_else(study_n %in% c("#1727", "#1302", "#1074", "#743", "#4403"), 1, 0),
         Era = factor(case_when(study_n %in% c("#1727", "#1302", "#743", "#896") ~ "2011-2020",
                         study_n %in% c("#3751", "#877", "#6317", "#6759") ~ "2021-2026",
                         study_n %in% c("#1074", "#699", "#4403") ~ "2001-2010")),
         Region = factor(case_when(study_n %in% c("#1727", "#1074", "#743", "#6317", "#6759") ~ "Europe and Central Asia",
                              study_n %in% c("#4403") ~ "Latin America and Carribean",
                              study_n %in% c("#1302") ~ "Sub-Saharan Africa",
                              study_n %in% c("#3751", "#877") ~ "East Asia and Pacific",
                              TRUE ~ "North America"))
         )

m_surcom <- metabin(
  event.e = e_men,
  n.e     = total_men,
  event.c = e_women,
  n.c     = total_women,
  studlab = study_id,
  data    = surcom_data,
  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_surcom)
```

#### Forest plot

```{r, fig.height=4, fig.width=12, warning=FALSE}
fp_surcom <- as.ggplot(~ forest(
  m_surcom,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_surcom

# ggsave("Plots/fp_surcom.pdf", fp_surcom, width = 12, height = 4, bg = "white")
```

##### Dataframe

```{r}
df_fp_surcom <- m_surcom$data %>%
  mutate(
    OR = exp(m_surcom$TE),
    lower_CI = exp(m_surcom$lower),
    upper_CI = exp(m_surcom$upper),
    weight_random = weights(m_surcom)$p.random
  ) %>%
  transmute(
    Study = study_id,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
  )
```

#### Funnel plot

```{r}
funnel(m_surcom)
```

#### SA excluding high RoB

```{r}
surcom_data_sa <- surcom_data %>%
  filter(high_rob == 0)

m_surcom_sa <- metabin(
  event.e = e_men,
  n.e     = total_men,
  event.c = e_women,
  n.c     = total_women,
  studlab = study_id,
  data    = surcom_data_sa,
  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_surcom_sa)
```

##### Forest plot

```{r, fig.height=4, fig.width=12, warning=FALSE}
fp_surcom_sa <- as.ggplot(~ forest(
  m_surcom_sa,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
)) + 
  ggtitle(label = "Surgical complications",
  subtitle = "Excluding studies with high risk of bias") +
  theme(
    plot.title = element_text(hjust = 0, size = 14, face = "bold"), 
    plot.subtitle = element_text(hjust = 0, size = 12), 
    margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm"))

fp_surcom_sa

# ggsave("Plots/fp_surcom_sa.pdf", fp_surcom_sa, width = 12, height = 4, bg = "white")
```

##### Dataframe

```{r}
df_fp_surcom_sa <- m_surcom_sa$data %>%
  mutate(
    OR = exp(m_surcom_sa$TE),
    lower_CI = exp(m_surcom_sa$lower),
    upper_CI = exp(m_surcom_sa$upper),
    weight_random = weights(m_surcom_sa)$p.random
  ) %>%
  transmute(
    Study = study_id,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
  )
```

#### By Time Era

```{r}
m_surcom_by_era <- metabin(
  event.e = e_men,
  n.e     = total_men,
  event.c = e_women,
  n.c     = total_women,
  studlab = study_id,
  data    = surcom_data,
  subgroup = Era,
  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_surcom_by_era)
```

##### Forest plot

```{r, fig.height=8, fig.width=12, warning=FALSE}
fp_surcom_by_era <- as.ggplot(~ forest(
  m_surcom_by_era,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_surcom_by_era

# ggsave("Plots/fp_surcom_by_era.pdf", fp_surcom_by_era, height = 8, width = 12, bg = "white")

```

##### Dataframe

```{r}
df_fp_surcom_by_era <- m_surcom_by_era$data %>%
  mutate(
    OR = exp(m_surcom_by_era$TE),
    lower_CI = exp(m_surcom_by_era$lower),
    upper_CI = exp(m_surcom_by_era$upper),
    weight_random = weights(m_surcom_by_era)$p.random
  ) %>%
  transmute(
    Era = Era,
    Study = study_id,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
    `Weight` = paste(round(weight_random, 1), "%")
  ) %>%
  arrange(Era)
```

#### By region

```{r}
m_surcom_by_region <- metabin(
  event.e = e_men,
  n.e     = total_men,
  event.c = e_women,
  n.c     = total_women,
  studlab = study_id,
  data    = surcom_data,
  subgroup = Region,
  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_surcom_by_region)
```

##### Forest plot

```{r, fig.height=9, fig.width=12, warning=FALSE}
fp_surcom_by_region <- as.ggplot(~ forest(
  m_surcom_by_region,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))


fp_surcom_by_region

# ggsave("Plots/fp_surcom_by_region.pdf", fp_surcom_by_region, height = 9, width = 12, bg = "white")
```

##### Dataframe

```{r}
df_fp_surcom_by_region <- m_surcom_by_region$data %>%
  mutate(
    OR = exp(m_surcom_by_era$TE),
    lower_CI = exp(m_surcom_by_era$lower),
    upper_CI = exp(m_surcom_by_era$upper),
    weight_random = weights(m_surcom_by_era)$p.random
  ) %>%
  transmute(
    Study = study_id,
    Region = Region,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
    `Weight` = paste(round(weight_random, 1), "%")
  ) %>%
  arrange(Region)
```

------------------------------------------------------------------------

### 5) Renal compensation

```{r}
renalcom_data <- read_xlsx("METANALYSIS DATA_new_latest.xlsx",
                 sheet = "rencom_data", skip = 1) %>% 
  filter(outcome == 2) %>%
  mutate(
    study_n = trimws(study_n),
    Era = factor(case_when(study_n %in% c("# 193", "#300", "#458", "#150")~ "2011-2020",
                           TRUE ~ "2021-2026")),
    Region = factor(case_when(
      study_n %in% c("# 193", "#150")~ "East Asia and Pacific",
      study_n %in% c("#458", "#7157", "#7961")~ "Europe and Central Asia",
      study_n == "#300" ~ "Middle-east, North-Africa, Afganistan and Pakistan",
      study_n == "#6926" ~ "Latin-America and Carribean",
      study_n == "#7873" ~ "South Asia"
    )))

m_renalcom <- metabin(
  event.e = e_men,
  n.e     = total_men,
  event.c = e_women,
  n.c     = total_women,
  studlab = study_id,
  data    = renalcom_data,
  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci")
)

summary(m_renalcom)
```

#### Forest plot

```{r, fig.height=4, fig.width=12, warning=FALSE}
fp_renalcom <- as.ggplot(~ forest(
  m_renalcom,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_renalcom

# ggsave("Plots/fp_renalcom.pdf", fp_renalcom, width = 12, height = 4, bg = "white")
```

```{r, include=FALSE}
sex_renalcom_or <- escalc(
  measure = "OR",
  ai = e_men, bi = ne_men,
  ci = e_women, di = ne_women,
  slab = paste(study_id),
  drop00 = TRUE,
  data = renalcom_data
)

sex_renalcom_res1 <- rma(yi, vi, data= sex_renalcom_or)

```

##### Dataframe

```{r}
df_fp_renalcom <- m_renalcom$data %>%
  mutate(
    OR = exp(m_renalcom$TE),
    lower_CI = exp(m_renalcom$lower),
    upper_CI = exp(m_renalcom$upper),
    weight_random = weights(m_renalcom)$p.random
  ) %>%
  transmute(
    Study = study_id,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
    `Weight` = paste(round(weight_random, 1), "%")
  )
```

#### By Era

```{r}
m_renalcom_era <- metabin(
  event.e = e_men,
  n.e     = total_men,
  event.c = e_women,
  n.c     = total_women,
  studlab = study_id,
  data    = renalcom_data,
  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci"),
  subgroup = Era
)

summary(m_renalcom_era)
```

##### Forest plot

```{r, fig.height=6, fig.width=12, warning=FALSE}
fp_renalcom_era <- as.ggplot(~ forest(
  m_renalcom_era,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_renalcom_era

# ggsave("Plots/fp_renalcom_era.pdf", fp_renalcom_era, width = 12, height = 6, bg = "white")
```

##### Dataframe

```{r}
df_fp_renalcom_era <- m_renalcom_era$data %>%
  mutate(
    OR = exp(m_renalcom$TE),
    lower_CI = exp(m_renalcom$lower),
    upper_CI = exp(m_renalcom$upper),
    weight_random = weights(m_renalcom)$p.random
  ) %>%
  transmute(
    Study = study_id,
    Era = Era,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
    `Weight` = paste(round(weight_random, 1), "%")
  )
```

#### By Region

```{r}
m_renalcom_region <- metabin(
  event.e = e_men,
  n.e     = total_men,
  event.c = e_women,
  n.c     = total_women,
  studlab = study_id,
  data    = renalcom_data,
  sm = "OR",
  method = "Inverse",
  method.tau = "REML",
  method.random.ci = gs("method.random.ci"),
  subgroup = Region
)

summary(m_renalcom_region)
```

##### Forest plot

```{r, fig.height=6, fig.width=12, warning=FALSE}
fp_renalcom_region <- as.ggplot(~ forest(
  m_renalcom_region,
  leftcols = c("studlab", "event.e", "n.e", "event.c", "n.c"),
  leftlabs = c(
    "Study",
    "Male\nEvents", 
    "Male\nTotal",
    "Female\nEvents", 
    "Female\nTotal"),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("Odds Ratio\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "1cm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "Odds Ratio\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_renalcom_region

# ggsave("Plots/fp_renalcom_region.pdf", fp_renalcom_region, width = 12, height = 6, bg = "white")
```

##### Dataframe

```{r}
df_fp_renalcom_region <- m_renalcom_region$data %>%
  mutate(
    OR = exp(m_renalcom$TE),
    lower_CI = exp(m_renalcom$lower),
    upper_CI = exp(m_renalcom$upper),
    weight_random = weights(m_renalcom)$p.random
  ) %>%
  transmute(
    Study = study_id,
    Region = Region,
    `Male Events` = e_men,
    `Male Total` = total_men,
    `Female Events` = e_women,
    `Female Total` = total_women,
    `Odds Ratio (Male vs Female)` = round(OR, 2),
    `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
    `Weight` = paste(round(weight_random, 1), "%")
  )
```

------------------------------------------------------------------------

### 6) QoL

Every study included on QoL have high risk of bias, so no sensitivity analysis was done.

#### Men

```{r}
qol_data <- read_excel("METANALYSIS DATA_new_latest.xlsx", sheet = "qol_data_mod", skip = 1) %>%
  filter(!is.na(study_id)) %>%
  mutate(
    across(everything(), ~replace(.x, .x == " " | .x == "" | .x== " ", NA)),
    study = trimws(as.character(study_id)),
    Era = factor(case_when(
      study_n %in% c("#4403") ~ "2001-2010",
      study_n %in% c("#5818", "#18", "#199", "#894", "#134") ~ "2011-2020",
      study_n %in% c("#7658") ~ "2021-2026")),
    Region = factor(case_when(
      study_n %in% c("#5818", "#18", "#199", "#7658", "#134") ~ "Europe and central Asia",
      study_n %in% c("#894") ~ "East Asia and Pacific",
      TRUE ~ "Latin-America and Carribean"))
    )

domains <- c("pcs","mcs","gh","sf","vi","bp","rp","pf","mh","re")

results_men_meta <- data.frame(
  domain = character(), k = integer(),
  pooled_mean = numeric(), ci_lb = numeric(), ci_ub = numeric(),
  I2 = numeric(), tau2 = numeric(),
  stringsAsFactors = FALSE
)

for (d in domains) {
  mean_col <- paste0(d, "_men_mean")
  sd_col   <- paste0(d, "_men_sd")

  sub <- qol_data %>%
    transmute(
      study = study,
      n = as.numeric(total_men),
      mean = as.numeric(.data[[mean_col]]),
      sd = as.numeric(.data[[sd_col]])
    ) %>%
    filter(complete.cases(.)) 

  if (nrow(sub) < 2) next

  m <- metamean(
    n = n,
    mean = mean,
    sd = sd,
    studlab = study,
    data = sub,
    sm = "MRAW",
    common = FALSE,
    random = TRUE,
    method.tau = "REML",
    method.random.ci = "classic"  # aligns with standard normal-approx random CI
  )

  results_men_meta <- rbind(
    results_men_meta,
    data.frame(
      domain = d,
      k = m$k,
      pooled_mean = as.numeric(m$TE.random),
      ci_lb = as.numeric(m$lower.random),
      ci_ub = as.numeric(m$upper.random),
      I2 = as.numeric(m$I2),
      tau2 = as.numeric(m$tau^2),
      stringsAsFactors = FALSE
    )
  )
}

results_men_meta
```

------------------------------------------------------------------------

#### Women

```{r}
results_women_meta <- data.frame(
  domain = character(), k = integer(),
  pooled_mean = numeric(), ci_lb = numeric(), ci_ub = numeric(),
  I2 = numeric(), tau2 = numeric(),
  stringsAsFactors = FALSE
)

for (d in domains) {
  mean_col <- paste0(d, "_women_mean")
  sd_col   <- paste0(d, "_women_sd")

  sub <- qol_data %>%
    transmute(
      study = study,
      n = as.numeric(total_women),
      mean = as.numeric(.data[[mean_col]]),
      sd = as.numeric(.data[[sd_col]])
    ) %>%
    filter(complete.cases(.)) 

  if (nrow(sub) < 2) next

  m <- metamean(
    n = n,
    mean = mean,
    sd = sd,
    studlab = study,
    data = sub,
    sm = "MRAW",
    common = FALSE,
    random = TRUE,
    method.tau = "REML",
    method.random.ci = "classic"  # aligns with standard normal-approx random CI
  )

  results_women_meta <- rbind(
    results_women_meta,
    data.frame(
      domain = d,
      k = m$k,
      pooled_mean = as.numeric(m$TE.random),
      ci_lb = as.numeric(m$lower.random),
      ci_ub = as.numeric(m$upper.random),
      I2 = as.numeric(m$I2),
      tau2 = as.numeric(m$tau^2),
      stringsAsFactors = FALSE
    )
  )
}

results_women_meta
```

------------------------------------------------------------------------

#### Standard mean difference

```{r}
results_smd_meta <- data.frame(
  domain = character(), k = integer(),
  SMD = numeric(), ci_lb = numeric(), ci_ub = numeric(),
  I2 = numeric(), tau2 = numeric(),
  stringsAsFactors = FALSE
)

for (d in domains) {

  m1 <- paste0(d, "_men_mean");   s1 <- paste0(d, "_men_sd")
  m2 <- paste0(d, "_women_mean"); s2 <- paste0(d, "_women_sd")

  sub <- qol_data %>%
    transmute(
      study  = study,
      n_men  = as.numeric(total_men),
      m_men  = as.numeric(.data[[m1]]),
      sd_men = as.numeric(.data[[s1]]),
      n_wom  = as.numeric(total_women),
      m_wom  = as.numeric(.data[[m2]]),
      sd_wom = as.numeric(.data[[s2]])
    ) %>%
    filter(complete.cases(.))

  if (nrow(sub) < 2) next

  m <- metacont(
    n.e = n_men, mean.e = m_men, sd.e = sd_men,
    n.c = n_wom, mean.c = m_wom, sd.c = sd_wom,
    studlab = study,
    data = sub,

    sm = "SMD",
    method.smd = "Hedges",
    common = FALSE,
    random = TRUE,
    method.tau = "REML",
    method.random.ci = "classic"
  )

  results_smd_meta <- rbind(
    results_smd_meta,
    data.frame(
      domain = d,
      k = m$k,
      SMD = as.numeric(m$TE.random),
      ci_lb = as.numeric(m$lower.random),
      ci_ub = as.numeric(m$upper.random),
      I2 = as.numeric(m$I2),
      tau2 = as.numeric(m$tau^2),
      stringsAsFactors = FALSE
    )
  )
}

results_smd_meta
```

------------------------------------------------------------------------

#### General Health

```{r}
dom <- "gh"

gh_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men= as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom= as.numeric(qol_data[[paste0(dom, "_women_sd")]]),
  Era = qol_data$Era,
  Region = qol_data$Region
) %>%
  filter(complete.cases(.))

m_gh <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = gh_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_gh
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_gh <- as.ggplot(~ forest(
  m_gh,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_gh

# ggsave("Plots/fp_gh.pdf", fp_gh, width = 13, height = 4, bg = "white")
```

##### By time era

```{r}
m_gh_era <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = gh_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Era
)

m_gh_era
```

###### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_gh_era <- as.ggplot(~ forest(
  m_gh_era,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_gh_era

# ggsave("Plots/fp_gh_era.pdf", fp_gh_era, width = 13, height = 4, bg = "white")
```

##### By region

```{r}
m_gh_region <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = gh_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Region
)

m_gh_region
```

###### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_gh_region <- as.ggplot(~ forest(
  m_gh_region,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_gh_region

# ggsave("Plots/fp_gh_region.pdf", fp_gh_region, width = 13, height = 4, bg = "white")
```

------------------------------------------------------------------------

#### Social functioning

```{r}
dom <- "sf"

sf_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men= as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom= as.numeric(qol_data[[paste0(dom, "_women_sd")]])
) %>%
  filter(complete.cases(.))

m_sf <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = sf_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_sf
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_sf <- as.ggplot(~ forest(
  m_sf,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_sf

# ggsave("Plots/fp_sf.pdf", fp_sf, width = 13, height = 4, bg = "white")
```

------------------------------------------------------------------------

#### Vitality

```{r}
dom <- "vi"

vi_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men= as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom= as.numeric(qol_data[[paste0(dom, "_women_sd")]]),
  Era = qol_data$Era,
  Region = qol_data$Region
) %>%
  filter(complete.cases(.))

m_vi <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = vi_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_vi
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_vi <- as.ggplot(~ forest(
  m_vi,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_vi

# ggsave("Plots/fp_vi.pdf", fp_vi, width = 13, height = 4, bg = "white")
```

##### By time era

```{r}
m_vi_era <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = vi_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Era
)

m_vi_era
```

###### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_vi_era <- as.ggplot(~ forest(
  m_vi_era,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_vi_era

# ggsave("Plots/fp_vi_era.pdf", fp_vi_era, width = 13, height = 4, bg = "white")
```

##### By region

```{r}
m_vi_region <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = vi_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Region
)

m_vi_region
```

###### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_vi_region <- as.ggplot(~ forest(
  m_vi_region,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_vi_region

# ggsave("Plots/fp_vi_region.pdf", fp_vi_region, width = 13, height = 4, bg = "white")
```

------------------------------------------------------------------------

#### Bodily pain

```{r}
dom <- "bp"

bp_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men= as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom= as.numeric(qol_data[[paste0(dom, "_women_sd")]])
) %>%
  filter(complete.cases(.))

m_bp <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = bp_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_bp
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_bp <- as.ggplot(~ forest(
  m_bp,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_bp

# ggsave("Plots/fp_bp.pdf", fp_bp, width = 13, height = 4, bg = "white")
```

------------------------------------------------------------------------

#### Role Physical

```{r}
dom <- "rp"

rp_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men= as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom= as.numeric(qol_data[[paste0(dom, "_women_sd")]])
) %>%
  filter(complete.cases(.))

m_rp <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = rp_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_rp
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_rp <- as.ggplot(~ forest(
  m_rp,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_rp

# ggsave("Plots/fp_rp.pdf", fp_rp, width = 13, height = 4, bg = "white")
```

------------------------------------------------------------------------

#### Physical functioning

```{r}
dom <- "pf"

pf_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men= as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom= as.numeric(qol_data[[paste0(dom, "_women_sd")]]),
  Era = qol_data$Era,
  Region = qol_data$Region
) %>%
  filter(complete.cases(.))

m_pf <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = pf_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_pf
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_pf <- as.ggplot(~ forest(
  m_pf,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_pf

# ggsave("Plots/fp_pf.pdf", fp_pf, width = 13, height = 4, bg = "white")
```

##### By time era

```{r}
m_pf_era <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = pf_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Era
)

m_pf_era
```

###### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_pf_era <- as.ggplot(~ forest(
  m_pf_era,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_pf_era

# ggsave("Plots/fp_pf_era.pdf", fp_pf_era, width = 13, height = 4, bg = "white")
```

##### By region

```{r}
m_pf_region <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = pf_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Region
)

m_pf_region
```

###### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_pf_region <- as.ggplot(~ forest(
  m_pf_region,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_pf_region

# ggsave("Plots/fp_pf_region.pdf", fp_pf_region, width = 13, height = 4, bg = "white")
```

------------------------------------------------------------------------

#### Mental health

```{r}
dom <- "mh"

mh_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men= as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom= as.numeric(qol_data[[paste0(dom, "_women_sd")]]),
  Era = qol_data$Era,
  Region = qol_data$Region
) %>%
  filter(complete.cases(.))

m_mh <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = mh_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_mh
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_mh <- as.ggplot(~ forest(
  m_mh,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_mh

# ggsave("Plots/fp_mh.pdf", fp_mh, width = 13, height = 4, bg = "white")
```

##### By time era

```{r}
m_mh_era <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = mh_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Era
)

m_mh_era
```

###### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_mh_era <- as.ggplot(~ forest(
  m_mh_era,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_mh_era

# ggsave("Plots/fp_mh_era.pdf", fp_mh_era, width = 13, height = 4, bg = "white")
```

##### By region

```{r}
m_mh_region <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = mh_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Region
)

m_mh_region
```

###### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_mh_region <- as.ggplot(~ forest(
  m_mh_region,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_mh_region

# ggsave("Plots/fp_mh_region.pdf", fp_mh_region, width = 13, height = 4, bg = "white")
```

------------------------------------------------------------------------

#### Role emotional

```{r}
dom <- "re"

re_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men= as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom= as.numeric(qol_data[[paste0(dom, "_women_sd")]])
) %>%
  filter(complete.cases(.))

m_re <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = re_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_re
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_re <- as.ggplot(~ forest(
  m_re,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,   digits = 2,   digits.sd = 2,   digits.mean = 2,   digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_re

# ggsave("Plots/fp_re.pdf", fp_re, width = 13, height = 4, bg = "white")
```

#### PCS

```{r}
dom <- "pcs"

pcs_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men = as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom = as.numeric(qol_data[[paste0(dom, "_women_sd")]]),
  Era = qol_data$Era,
  Region = qol_data$Region
) %>%
  filter(complete.cases(.))

m_pcs <- metacont(
  n.e = n_men,
  mean.e = m_men,
  sd.e = sd_men,
  n.c = n_wom,
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = pcs_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_pcs
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_pcs <- as.ggplot(~ forest(
  m_pcs,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,
  digits = 2,
  digits.sd = 2,
  digits.mean = 2,
  digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square = "#82abc4",
  col.diamond = "#285980",
  col.study.ci = "black",
  col.inside = "black"
))

fp_pcs

# ggsave("Plots/fp_pcs.pdf", fp_pcs, width = 13, height = 4, bg = "white")
```

##### By Era

```{r}
m_pcs_era <- metacont(
  n.e = n_men,  
  mean.e = m_men,  
  sd.e = sd_men,
  n.c = n_wom,  
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = pcs_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Era
)

m_pcs_era
```

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_pcs_era <- as.ggplot(~ forest(
  m_pcs_era,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,
  digits = 2,
  digits.sd = 2,
  digits.mean = 2,
  digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_pcs_era
```

##### By Region

```{r}
m_pcs_region <- metacont(
  n.e = n_men,
  mean.e = m_men,
  sd.e = sd_men,
  n.c = n_wom,
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = pcs_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Region
)

m_pcs_region
```

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_pcs_region <- as.ggplot(~ forest(
  m_pcs_region,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,
  digits = 2,
  digits.sd = 2,
  digits.mean = 2,
  digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_pcs_region
```

#### MCS

```{r}
dom <- "mcs"

mcs_data <- data.frame(
  study = qol_data$study,
  n_men = as.numeric(qol_data$total_men),
  m_men = as.numeric(qol_data[[paste0(dom, "_men_mean")]]),
  sd_men = as.numeric(qol_data[[paste0(dom, "_men_sd")]]),
  n_wom = as.numeric(qol_data$total_women),
  m_wom = as.numeric(qol_data[[paste0(dom, "_women_mean")]]),
  sd_wom = as.numeric(qol_data[[paste0(dom, "_women_sd")]]),
  Era = qol_data$Era,
  Region = qol_data$Region
) %>%
  filter(complete.cases(.))

m_mcs <- metacont(
  n.e = n_men,
  mean.e = m_men,
  sd.e = sd_men,
  n.c = n_wom,
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = mcs_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic"
)

m_mcs
```

##### Forest plot

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_mcs <- as.ggplot(~ forest(
  m_mcs,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,
  digits = 2,
  digits.sd = 2,
  digits.mean = 2,
  digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square = "#82abc4",
  col.diamond = "#285980",
  col.study.ci = "black",
  col.inside = "black"
))

fp_mcs

# ggsave("Plots/fp_mcs.pdf", fp_mcs, width = 13, height = 4, bg = "white")
```

##### By Era

```{r}
m_mcs_era <- metacont(
  n.e = n_men,
  mean.e = m_men,
  sd.e = sd_men,
  n.c = n_wom,
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = mcs_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Era
)

m_mcs_era
```

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_mcs_era <- as.ggplot(~ forest(
  m_mcs_era,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,
  digits = 2,
  digits.sd = 2,
  digits.mean = 2,
  digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_mcs_era
```

##### By Region

```{r}
m_mcs_region <- metacont(
  n.e = n_men,
  mean.e = m_men,
  sd.e = sd_men,
  n.c = n_wom,
  mean.c = m_wom,
  sd.c = sd_wom,
  studlab = study,
  data = mcs_data,
  sm = "SMD",
  method.smd = "Hedges",
  common = FALSE,
  random = TRUE,
  method.tau = "REML",
  method.random.ci = "classic",
  subgroup = Region
)

m_mcs_region
```

```{r, fig.height=4, fig.width=13, warning=FALSE}
fp_mcs_region <- as.ggplot(~ forest(
  m_mcs_region,
  leftcols = c("studlab", "n.e", "mean.e", "sd.e", "n.c", "mean.c", "sd.c"),
  leftlabs = c(
    "Study",
    "Male\nN", "Male\nMean", "Male\nSD",
    "Female\nN", "Female\nMean", "Female\nSD"
  ),
  rightcols = c("effect", "ci", "w.random"),
  rightlabs = c("SMD\n(Male vs Female)", "95% CI", "Weight"),
  colgap = "6mm",
  print.I2 = TRUE,
  print.tau2 = TRUE,
  print.Q = TRUE,
  overall = TRUE,
  digits = 2,
  digits.sd = 2,
  digits.mean = 2,
  digits.weight = 2,
  overall.hetstat = TRUE,
  label.e = "Male",
  label.c = "Female",
  smlab = "SMD\n(Male vs Female)",
  col.square   = "#82abc4",
  col.diamond  = "#285980",
  col.study.ci = "black",
  col.inside   = "black"
))

fp_mcs_region
```

------------------------------------------------------------------------

## Combined forest plot

[BMJ guide](https://bmjmedicine.bmj.com/bmjmedicine/wp-content/uploads/sites/66/2023/06/BMJMED-style-formatting-checklist-for-original-research-pre-acceptance-1.pdf)

**IMPORTANT FOR FOREST PLOT FIGURES:** Provide typed out data for any forest plots in a table format in a Word document (see Appendix 3), to avoid the introduction of errors when figures are redrawn.\
These data are not the underlying data that make up the plots themselves, but are the actual numbers that appear next to the forest plots in the figure. Do not provide typed out data for forest plots in web only material. Present confidence intervals in the format “xx to xx” (not “xx, xx” or “xx-xx”)

### F3) Main outcomes

```{r, fig.height=13.5, fig.width=12, warning=FALSE}
blank <- ggplot() + theme_void()

main_f1 <- ggarrange(
  fp_death + ggtitle("A) Mortality") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_kf + ggtitle("B) Kidney failure") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_gfr + ggtitle("C) Chronic kidney disease") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_renalcom + ggtitle("D) Renal compensation") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"),margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  ncol = 1,
  heights = c(0.7, 0.03, 0.7, 0.03, 0.9, 0.03, 0.8)
  )

main_f1
# ggsave("Plots/F3_ForestPlots.pdf", main_f1, width = 12, height = 13.5, bg = "white")
# ggsave("Final plots/F3_ForestPlots.pdf", main_f1, width = 12, height = 13.5, bg = "white")
```

#### Dataframe

Export the data for redrawing as per BMJ requirements:

```{r}
write_xlsx(
  list(
    Mortality = df_fp_mor,
    Kidney_Failure = df_fp_kf,
    CKD = df_fp_gfr,
    Renal_Compensation = df_fp_renalcom
  ),
  "Forest_Plots_Data/Figure_3_data.xlsx"
)
```

### Supp.F1) Sensitivity analyses

```{r, fig.height=6.5, fig.width=12}
supp_f1_fp_rob <- ggarrange(
  fp_death_sa + ggtitle("A) Mortality: Excluding studies with high risk of bias") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold", margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"))),
  blank,
  fp_gfr_sa + ggtitle("B) Chronic kidney disease: Excluding a large study") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold", margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"))),
  ncol = 1,
  heights = c(0.75, 0.1, 1)
  )

supp_f1_fp_rob

# ggsave("Plots/Supp_f1_SA.pdf", supp_f1_fp_rob, width = 12, height = 6.5, bg = "white")
# ggsave("Final plots/Supp_f1_SA.pdf", supp_f1_fp_rob, width = 12, height = 6.5, bg = "white")
```

### Supp.F4) Surgical outcomes

```{r, fig.height=8, fig.width=12}
supp_f2_surcom <- ggarrange(
  fp_surcom + ggtitle("A) Surgical complications") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold", margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"))),
  blank,
  fp_surcom_sa + ggtitle("B) Surgical complications") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold", margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"))),
  # blank,
  # fp_surcom_by_era + ggtitle("C) Surgical complications") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold", margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"))),
  ncol = 1,
  heights = c(0.9, 0.05, 0.75)
  )

supp_f2_surcom

# ggsave("Plots/Supp_f4_surcom.pdf", supp_f2_surcom, width = 12, height = 8, bg = "white")
# ggsave("Final plots/Supp_f4_surcom.pdf", supp_f2_surcom, width = 12, height = 8, bg = "white")
```

#### Dataframe

```{r}
write_xlsx(
  list(
    Surcom = df_fp_surcom,
    SensitivityAnalysis = df_fp_surcom_sa
    # By_era = df_fp_surcom_by_era
  ),
  "Forest_Plots_Data/S4_SurCom_fp_data.xlsx"
)
```

------------------------------------------------------------------------

### Supp.F6) QoL

```{r, fig.height=15, fig.width=26, warning=FALSE}
# 2 columns

blank <- ggplot() + theme_void()

main_f2_v2 <- ggarrange(
  fp_gh + ggtitle("A) General health") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  fp_sf + ggtitle("B) Social functioning") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  fp_vi + ggtitle("C) Vitality") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  fp_bp + ggtitle("D) Bodily pain") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  fp_rp + ggtitle("E) Role physical") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  fp_pf + ggtitle("F) Physical functioning") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  fp_mh + ggtitle("G) Mental health") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  fp_re + ggtitle("H) Role emotional") + theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  fp_pcs + ggtitle("I) Physical component summary") +
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"),
          margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  fp_mcs + ggtitle("J) Mental component summary") +
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"),
          margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),
  ncol = 2,
  nrow = 5
  )

main_f2_v2

# ggsave("Plots/Supp_F6_QoL_ForestPlots.pdf", main_f2_v2, width = 26, height = 15, bg = "white")
# ggsave("Final plots/Supp_F6_QoL_ForestPlots.pdf", main_f2_v2, width = 26, height = 15, bg = "white")

ggsave(
  "Final plots/Supp_F6_QoL_ForestPlots.jpg",
  main_f2_v2,
  width = 26,
  height = 15,
  units = "in",
  dpi = 300,
  bg = "white"
)
```

#### Dataframe

```{r}
extract_smd_df <- function(meta_obj,
                           effect_label = "SMD (Male vs Female)") {
  
  meta_obj$data %>%
    mutate(
      SMD = meta_obj$TE,
      lower_CI = meta_obj$lower,
      upper_CI = meta_obj$upper,
      weight_random = weights(meta_obj)$p.random
    ) %>%
    transmute(
      Study = study,
      `Male N` = n_men,
      `Male Mean` = m_men,
      `Male SD` = sd_men,
      `Female N` = n_wom,
      `Female Mean` = m_wom,
      `Female SD` = sd_wom,
      !!effect_label := round(SMD, 2),
      `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
    )
}

df_fp_gh <- extract_smd_df(m_gh)
df_fp_sf <- extract_smd_df(m_sf)
df_fp_vi <- extract_smd_df(m_vi)
df_fp_bp <- extract_smd_df(m_bp)

df_fp_rp <- extract_smd_df(m_rp)
df_fp_pf <- extract_smd_df(m_pf)
df_fp_mh <- extract_smd_df(m_mh)
df_fp_re <- extract_smd_df(m_re)

write_xlsx(
  list(
    GeneralHealth = df_fp_gh,
    SocialFunctioning = df_fp_sf,
    Vitality = df_fp_vi,
    BodilyPain = df_fp_bp,
    RolePhysical = df_fp_rp,
    Physicalfunctioning = df_fp_pf,
    MentalHealth = df_fp_mh,
    RoleEmptional = df_fp_re
  ),
  "Forest_Plots_Data/S6_QoL_fp_data.xlsx"
)
```

------------------------------------------------------------------------

### Supp. F2) Subgroup by era

```{r, fig.height=19, fig.width=12, warning=FALSE}
blank <- ggplot() + theme_void()

fp_by_era <- ggarrange(
  fp_gfr_era + ggtitle("A) Chronic kidney disease") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_surcom_by_era + ggtitle("B) Surgical complications") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_renalcom_era + ggtitle("C) Renal compensation") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  ncol = 1,
  heights = c(1.15, 0.03, 1.4, 0.03, 1)
  )

fp_by_era
# ggsave("Plots/Supp_f2_by_era.pdf", fp_by_era, width = 12, height = 19, bg = "white")
# ggsave("Final plots/Supp_f2_by_era.pdf", fp_by_era, width = 12, height = 19, bg = "white")
```

#### Dataframe

Export the data for redrawing as per BMJ requirements:

```{r}
write_xlsx(
  list(
    CKD_Era = df_fp_gfr_era,
    Surcom_Era = df_fp_surcom_by_era,
    Renal_Compensation_Era = df_fp_renalcom_era,
    CKD_Region = df_fp_gfr_region,
    Surcom_Region = df_fp_surcom_by_region,
    Renal_Compensation_Region = df_fp_renalcom_region
  ),
  "Forest_Plots_Data/S2-3_Subgroup_MainOutcomes.xlsx"
)
```

------------------------------------------------------------------------

### Supp. F3) Subgroup by Region

```{r, fig.height=21, fig.width=12, warning=FALSE}
blank <- ggplot() + theme_void()

fp_by_region <- ggarrange(
  fp_gfr_region + ggtitle("A) Chronic kidney disease") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_surcom_by_region + ggtitle("B) Surgical complications") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_renalcom_region + ggtitle("C) Renal compensation") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  ncol = 1,
  heights = c(1.15, 0.03, 1.4, 0.03, 1)
  )

fp_by_region

# ggsave("Plots/Supp_f3_by_region.pdf", fp_by_region, width = 12, height = 21, bg = "white")
# ggsave("Final plots/Supp_f3_by_region.pdf", fp_by_region, width = 12, height = 21, bg = "white")
```

------------------------------------------------------------------------

### Supp. F7) QoL by Era

```{r, fig.height=18, fig.width=13, warning=FALSE}
blank <- ggplot() + theme_void()

fp_qol_by_era <- ggarrange(
  fp_gh_era + ggtitle("A) General health") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_vi_era + ggtitle("B) Vitality") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_pf_era + ggtitle("C) Physical functioning") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_mh_era + ggtitle("D) Mental health") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  ncol = 1,
  heights = c(1, 0.03, 1, 0.03, 1, 0.03, 1)
  )

fp_qol_by_era

# ggsave("Plots/Supp_f7_qol_by_era.pdf", fp_qol_by_era, width = 13, height = 18, bg = "white")
# ggsave("Final plots/Supp_f7_qol_by_era.pdf", fp_qol_by_era, width = 13, height = 18, bg = "white")
```

#### Dataframe

```{r}
extract_smd_df_era <- function(meta_obj,
                           effect_label = "SMD (Male vs Female)") {
  
  meta_obj$data %>%
    mutate(
      SMD = meta_obj$TE,
      lower_CI = meta_obj$lower,
      upper_CI = meta_obj$upper,
      weight_random = weights(meta_obj)$p.random
    ) %>%
    transmute(
      Era = Era,
      Study = study,
      `Male N` = n_men,
      `Male Mean` = m_men,
      `Male SD` = sd_men,
      `Female N` = n_wom,
      `Female Mean` = m_wom,
      `Female SD` = sd_wom,
      !!effect_label := round(SMD, 2),
      `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
    )
}

extract_smd_df_region <- function(meta_obj,
                           effect_label = "SMD (Male vs Female)") {
  
  meta_obj$data %>%
    mutate(
      SMD = meta_obj$TE,
      lower_CI = meta_obj$lower,
      upper_CI = meta_obj$upper,
      weight_random = weights(meta_obj)$p.random
    ) %>%
    transmute(
      Region = Region,
      Study = study,
      `Male N` = n_men,
      `Male Mean` = m_men,
      `Male SD` = sd_men,
      `Female N` = n_wom,
      `Female Mean` = m_wom,
      `Female SD` = sd_wom,
      !!effect_label := round(SMD, 2),
      `95% CI` = sprintf("[%.2f; %.2f]", lower_CI, upper_CI),
      `Weight` = paste0(round(weight_random, 1), "%")
    )
}

df_fp_gh_era <- extract_smd_df_era(m_gh_era)
df_fp_vi_era <- extract_smd_df_era(m_vi_era)
df_fp_pf_era <- extract_smd_df_era(m_pf_era)
df_fp_mh_era <- extract_smd_df_era(m_mh_era)

df_fp_gh_region <- extract_smd_df_region(m_gh_era)
df_fp_vi_region <- extract_smd_df_region(m_vi_region)
df_fp_pf_region <- extract_smd_df_region(m_pf_region)
df_fp_mh_region <- extract_smd_df_region(m_mh_region)

write_xlsx(
  list(
    GeneralHealth_Era = df_fp_gh_era,
    Vitality_Era = df_fp_vi_era,
    Physicalfunctioning_Era = df_fp_pf_era,
    MentalHealth_Era = df_fp_mh_era,
    GeneralHealth_Region = df_fp_gh_region,
    Vitality_Region = df_fp_vi_region,
    Physicalfunctioning_Region = df_fp_pf_region,
    MentalHealth_Region = df_fp_mh_region
  ),
  "Forest_Plots_Data/S7-8_QoL_Subgroup_data.xlsx"
)
```

------------------------------------------------------------------------

### Supp. F8) QoL by Region

```{r, fig.height=16.5, fig.width=13, warning=FALSE}
blank <- ggplot() + theme_void()

fp_qol_by_region <- ggarrange(
  fp_gh_region + ggtitle("A) General health") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_vi_region + ggtitle("B) Vitality") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_pf_region + ggtitle("C) Physical functioning") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  blank,
  fp_mh_region + ggtitle("D) Mental health") + 
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"), margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")),
  ncol = 1,
  heights = c(1, 0.03, 1, 0.03, 1, 0.03, 1)
  )

fp_qol_by_region

# ggsave("Plots/Supp_f8_qol_by_region.pdf", fp_qol_by_region, width = 13, height = 16.5, bg = "white")
# ggsave("Final plots/Supp_f8_qol_by_region.pdf", fp_qol_by_region, width = 13, height = 16.5, bg = "white")
```

### PCS & MCS Subgroup analyses

```{r, fig.height=9, fig.width=26, warning=FALSE}
combined_pcs_mcs_subgroups <- ggarrange(
  fp_pcs_era + ggtitle("A) PCS by reporting era") +
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"),
          margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),

  fp_pcs_region + ggtitle("B) PCS by region") +
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"),
          margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),

  fp_mcs_era + ggtitle("C) MCS by reporting era") +
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"),
          margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),

  fp_mcs_region + ggtitle("D) MCS by region") +
    theme(plot.title = element_text(hjust = 0, size = 14, face = "bold"),
          margin = margin(t = 1, r = 0, b = 0.5, l = 0, unit = "cm")),

  ncol = 2,
  nrow = 2
)

combined_pcs_mcs_subgroups

# ggsave(
#   "Final plots/PCS_MCS_Subgroup_Analyses.jpg",
#   combined_pcs_mcs_subgroups,
#   width = 26,
#   height = 9,
#   units = "in",
#   dpi = 300,
#   bg = "white"
# )
```
